PineAPPL:\\ combining EW and QCD corrections for PDF fits

### 2020-08-10 paper/sec-conclusion.tex
Replace 'mixed' with 'combined'

\section{Conclusions and Outlook}
\label{sec:conclusion}

@@

A distinguishing feature of \textsc{PineAPPL} is the support for arbitrary coupling orders not only in the strong, but also in the electroweak coupling.
This enables us to generate, for the first time, NLO EW and NLO mixed QCD--EW interpolation grids.
Using \textsc{mg5\_aMC@NLO} we calculated and showcased the impact of these corrections for important PDF processes for specific analyses from ATLAS and CMS: Drell--Yan lepton-pair production, top-pair production, and Z-boson production with non-zero transverse momentum.

Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolation grids with the corresponding experimental data in a PDF fit including EW and mixed QCD--EW corrections.

Having developed and thoroughly tested \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first global PDF fit including EW and mixed QCD--EW corrections.
This will have at least two advantages: in PDF fits phase-space regions are usually cut away if they exhibit large EW corrections; including them therefore increases the number of data points in a fit and therefore indirectly enlarges a PDF set's interpolation region.
Secondly, this makes it possible to use experimental data that are closer to the actual measurement, without the need to compensate for missing EW corrections.

>>>>

\section{Conclusions and Outlook}
\label{sec:conclusion}
{\bf MZ I would like to have some sort of introduction here (a short bla bla on precision), before turning to Pineappl}

@@

A distinguishing feature of \textsc{PineAPPL} is the support for arbitrary coupling orders not only in the strong, but also in the electroweak coupling.
This enables us to generate, for the first time, NLO EW and NLO combined QCD--EW interpolation grids.
Using \textsc{mg5\_aMC@NLO} we calculated and showcased the impact of these corrections for important PDF processes for specific analyses from ATLAS and CMS: Drell--Yan lepton-pair production, top-pair production, and Z-boson production with non-zero transverse momentum.

Finally, we discussed the issue of subtracting EW corrections in experimental data, which becomes an important consideration when combining the interpolation grids with the corresponding experimental data in a PDF fit including EW and combined QCD--EW corrections.

Having developed and thoroughly tested \textsc{PineAPPL}, all technical requirements are fulfilled for producing the first global PDF fit including EW and combined QCD--EW corrections.
This will have at least two advantages: in PDF fits phase-space regions are usually cut away if they exhibit large EW corrections; including them therefore increases the number of data points in a fit and therefore indirectly enlarges a PDF set's interpolation region.
Secondly, this makes it possible to use experimental data that are closer to the actual measurement, without the need to compensate for missing EW corrections.

### 2020-08-10 paper/sec-introduction.tex
Replace 'mixed' with 'combined'

In the first respect, because Quantum Chromodynamics (QCD) dominates the 
interactions occurring within colliding protons at the LHC, much effort 
has been devoted to the computation of higher-order QCD corrections: 
fully-differential next-to-leading order (NLO) results, possibly matched to a
parton shower, are currently automated in various general-purpose
Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}
(see also ref.~\cite{Buckley:2011ms} for a review),
while an increasing number of next-to-next-to-leading order (NNLO) predictions 
are becoming available for processes with various degrees of inclusiveness
(see e.g.\ ref.~\cite{Amoroso:2020lgh} and references therein). The computation
of higher-order corrections in the electroweak (EW) and mixed QCD+EW theory has
also witnessed a comprehensive progress. Frameworks 
were developed in which the QCD and EW couplings are simultaneously treated as 
small parameters in the perturbative expansion, and the computation of 
theoretical predictions, accurate to NLO in both (including mixed-coupling 
QCD--EW terms), is automated~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq}. For an extensive and recent review, see ref.~\cite{Denner:2019vbn}.

@@

The two respects are intertwined: PDFs provide a way of obtaining a prediction
for a given process in terms of other processes, therefore the accuracy and 
precision with which PDFs are able to make predictions crucially depend on 
the accuracy of the perturbative computation used in the PDF determination
(matched to the precision of the data). Electroweak (including mixed QCD+EW) 
effects should therefore naturally be included in a PDF determination. The 
reason is twofold. First, one expects NNLO QCD and NLO EW corrections to be of 
comparable size because, at the EW scale, the QCD and EW running couplings 
become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
by default in PDF determinations, NLO EW corrections should be
taken into account on the same footing. Second, the virtual exchange of soft or 
collinear weak bosons leads to Sudakov 
logarithms~\cite{Denner:2000jv,Denner:2001gw},
which can make the coefficients of the EW series grow faster than 
their QCD counterparts. Such a behaviour becomes relevant in
phase-space regions associated with large mass scales (roughly of the order
of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ Z-boson
transverse-momentum distributions) enter both the determination of PDFs and the search
for new physics.

>>>>

In the first respect, because Quantum Chromodynamics (QCD) dominates the 
interactions occurring within colliding protons at the LHC, much effort 
has been devoted to the computation of higher-order QCD corrections: 
fully-differential next-to-leading order (NLO) results, possibly matched to a
parton shower, are currently automated in various general-purpose
Monte Carlo generators~\cite{Gleisberg:2008ta,Alwall:2014hca,Bellm:2015jjp}
(see also ref.~\cite{Buckley:2011ms} for a review),
while an increasing number of next-to-next-to-leading order (NNLO) predictions 
are becoming available for processes with various degrees of inclusiveness
(see e.g.\ ref.~\cite{Amoroso:2020lgh} and references therein). The computation
of higher-order corrections in the electroweak (EW) and combined QCD+EW theory has
also witnessed a comprehensive progress. Frameworks 
were developed in which the QCD and EW couplings are simultaneously treated as 
small parameters in the perturbative expansion, and the computation of 
theoretical predictions, accurate to NLO in both (including multi-coupling
QCD--EW terms), is automated~\cite{Kallweit:2014xda,Biedermann:2017yoi,Frederix:2018nkq}. For an extensive and recent review, see ref.~\cite{Denner:2019vbn}.

@@

The two respects are intertwined: PDFs provide a way of obtaining a prediction
for a given process in terms of other processes, therefore the accuracy and 
precision with which PDFs are able to make predictions crucially depend on 
the accuracy of the perturbative computation used in the PDF determination
(matched to the precision of the data). Electroweak (including combined QCD--EW) 
effects should therefore naturally be included in a PDF determination. The 
reason is twofold. First, one expects NNLO QCD and NLO EW corrections to be of 
comparable size because, at the EW scale, the QCD and EW running couplings 
become similar, $\alphas^2\sim \alpha$. If NNLO QCD corrections are included
by default in PDF determinations, NLO EW corrections should be
taken into account on the same footing. Second, the virtual exchange of soft or 
collinear weak bosons leads to Sudakov 
logarithms~\cite{Denner:2000jv,Denner:2001gw},
which can make the coefficients of the EW series grow faster than 
their QCD counterparts. Such a behaviour becomes relevant in
phase-space regions associated with large mass scales (roughly of the order
of the \si{\tera\electronvolt}), where several LHC data sets (e.g.\ Z-boson
transverse-momentum distributions) enter both the determination of PDFs and the search
for new physics.

### 2020-08-10 paper/sec-pineappl.tex
Replace 'mixed' with 'combined'

The convolution is typically done in a few seconds or less, which offers at least two applications:
\begin{enumerate}
\item the study of PDF-dependence of observables; e.g.\ PDF set comparisons, PDF uncertainties for different PDF set, $\alphas$ variations, etc., and
\item the determination of PDF sets themselves; the grids together with the corresponding experimental data constitute two important ingredients for a PDF fit.
\end{enumerate}
This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to EW, and in general mixed QCD--EW, effects.
Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.

In particular, the following features are supported:
\begin{itemize}
\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including mixed QCD--EW corrections.
\item The support for non-coloured initial-state partons, such as photon-initiated contributions.
In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
\item The estimate of theory uncertainties via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
\end{itemize}
On a more technical level, we further point out the following differences and improvements in \textsc{PineAPPL}:
\begin{itemize}
\item \textsc{APPLgrid} typically required a substantial amount of memory (close to \SI{120}{\giga\byte} for Drell--Yan), if a grid for a differential distributions with more than 10 bins was generated.
The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
However, this required a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
\textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.
\item \textsc{PineAPPL} offers an easy-to-use interface written in the C programming language, to allow MC integrators to read and write \textsc{PineAPPL} grids.
C was chosen because it can be easily interfaced with both Fortran and C++, in which most MC integrators are written.
The interface consists of roughly 30 functions, among which only a handful are needed in practice.
See appendix~\ref{app:example-program} for an example.
\item The shell command \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
In addition to convolutions, it can also print how the luminosity function is constructed, which perturbative orders are stored, their size, the size of each partonic channel, etc., separately for each bin.
%\item Possibility to import \textsc{APPLgrids} and \textsc{fastNLO} tables.
\end{itemize}

@@

In general, we define leading order (LO) as the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
This number is process dependent and usually determined by the number of external particles.
For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
An important example at the LHC is (on-shell) top-pair production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
Each LO receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
All remaining corrections are of mixed type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin. However, for the sake of simplicity and with a slight abuse of notation, it is customary to refer 
as NLO QCD (EW) corrections as
corrections of order $\alphas$ ($\alpha$) times the couplings of the LO contribution 
with the largest power of $\alphas$. In the example above, NLO QCD and EW corrections to top pair production will denote
respectively those at $\mathcal{O} (\alphas^3 )$ and $\mathcal{O} (\alphas^2 \alpha)$. In this paper, in particular
when discussing results in sec.~\ref{sec:results}, we will explicitly list the orders that are considered in the cross
section at LO, NLO QCD and NLO QCD+EW accuracy.
%Sometimes there are higher orders that cannot directly be understood as a correction to a LO, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one LO, $\mathcal{O} (\alphas \alpha^2)$, but three NLOs, one of which is $\mathcal{O} (\alpha^4)$~TODO.

@@

Since this process has a single LO, mixed QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single mixed correction at $\mathcal{O} (\alphas \alpha^3)$.

Note that all initial states have to be taken into account that lead to the same final state.
This includes the photon--photon initial state, which appears already at LO.
In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW and mixed QCD--EW corrections, but never (pure) QCD corrections.
The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.

>>>>

The convolution is typically done in a few seconds or less, which offers at least two applications:
\begin{enumerate}
\item the study of PDF-dependence of observables; e.g.\ PDF set comparisons, PDF uncertainties for different PDF set, $\alphas$ variations, etc., and
\item the determination of PDF sets themselves; the grids together with the corresponding experimental data constitute two important ingredients for a PDF fit.
\end{enumerate}
This puts \textsc{PineAPPL} in the same category as \textsc{APPLgrid}~\cite{Carli:2010rw} and \textsc{fastNLO}~\cite{Kluge:2006xs,Wobisch:2011ij,Britzger:2012bs}.
With respect to the capabilities of these computer codes, \textsc{PineAPPL} makes it possible for the first time to include also higher-order corrections due to EW, and in general combined QCD--EW, effects.
Documenting this extension, and how to interface \textsc{PineAPPL} with a general-purpose matrix-element generator, is the main interest of this paper.

In particular, the following features are supported:
\begin{itemize}
\item The inclusion of perturbative corrections (fixed-order, i.e.\ without parton-shower matching) with any given set of powers of $\alpha$, $\alphas$, in particular including combined QCD--EW corrections.
\item The support for non-coloured initial-state partons, such as photon-initiated contributions.
In fact, \textsc{PineAPPL} allows arbitrary initial-state combinations, e.g.\ leptonic initial states~\cite{Bertone:2015lqa,Buonocore:2020nai}.
\item The estimate of theory uncertainties via variations of the renormalisation and factorisation scale (the electroweak coupling is assumed to be scale-independent, consistently with the most common renormalisation schemes).
\end{itemize}
On a more technical level, we further point out the following differences and improvements in \textsc{PineAPPL}:
\begin{itemize}
\item \textsc{APPLgrid} typically required a substantial amount of memory (close to \SI{120}{\giga\byte} for Drell--Yan), if a grid for a differential distributions with more than 10 bins was generated.
The memory usage is substantially reduced (roughly \SI{1}{\giga\byte}) after \enquote{optimisation} of the grids, i.e.\ an optimisation of the grid representation in memory.
However, this required a two-step procedure: first, to produce an unoptimised grid in order to identify those parts where the cross section is either zero or extremely suppressed; second, after those parts are removed, to fill an optimised grid with a small number of bins.
\textsc{PineAPPL} avoids this by using a more space-efficient representation from the start.
\item \textsc{PineAPPL} offers an easy-to-use interface written in the C programming language, to allow MC integrators to read and write \textsc{PineAPPL} grids.
C was chosen because it can be easily interfaced with both Fortran and C++, in which most MC integrators are written.
The interface consists of roughly 30 functions, among which only a handful are needed in practice.
See appendix~\ref{app:example-program} for an example.
\item The shell command \texttt{pineappl}, which performs convolutions on the command line (see appendix~\ref{app:pineappl-demo}), without requiring the user to write a new program.
In addition to convolutions, it can also print how the luminosity function is constructed, which perturbative orders are stored, their size, the size of each partonic channel, etc., separately for each bin.
%\item Possibility to import \textsc{APPLgrids} and \textsc{fastNLO} tables.
\end{itemize}

@@

In general, we define leading order (LO) as the set of contributions for all possible initial states $a b$ that lead to the same final state $X$, for which the sum of the coupling exponents in eq.~\eqref{eq:expansion} is smallest, i.e.\ $k + l = p$, where $p = \min (k+l)$.
This number is process dependent and usually determined by the number of external particles.
For many processes there is only one LO, but when a process has multiple quark lines, colourless (photons, \dots) and coloured particles (gluons, \ldots) can be exchanged between them, making it possible to have more than one LO.
An important example at the LHC is (on-shell) top-pair production, which has three different LOs: $\mathcal{O} (\alpha^2)$, $\mathcal{O} (\alphas \alpha)$, and $\mathcal{O} (\alpha^2)$.
Each LO receives a higher-order correction with an additional power of $\alphas$ or $\alpha$, which in general leads to at least two next-to-leading order (NLO) corrections.
The correction with the largest power in $\alphas$ can be unambiguously called \enquote{the} QCD correction, and the one with the largest power in $\alpha$ \enquote{the} EW correction.
All remaining corrections are of combined type, meaning that they, in general, cannot be attributed to either one of strong or electroweak origin. However, for the sake of simplicity and with a slight abuse of notation, it is customary to refer
as NLO QCD (EW) corrections as
corrections of order $\alphas$ ($\alpha$) times the couplings of the LO contribution 
with the largest power of $\alphas$. In the example above, NLO QCD and EW corrections to top pair production will denote
respectively those at $\mathcal{O} (\alphas^3 )$ and $\mathcal{O} (\alphas^2 \alpha)$. In this paper, in particular
when discussing results in sec.~\ref{sec:results}, we will explicitly list the orders that are considered in the cross
section at LO, NLO QCD and NLO QCD+EW accuracy.
%Sometimes there are higher orders that cannot directly be understood as a correction to a LO, e.g.\ $\mathrm{p} \mathrm{p} \to \ell \bar{\ell} + \mathrm{jet} + X$, which has one LO, $\mathcal{O} (\alphas \alpha^2)$, but three NLOs, one of which is $\mathcal{O} (\alpha^4)$~TODO.

@@

Since this process has a single LO, combined QCD--EW corrections first appear at next-to-next-to-leading order (NNLO), which include the QCD correction at $\mathcal{O} (\alphas^2 \alpha^2)$, the EW correction $\mathcal{O} (\alpha^4)$, and a single combined correction at $\mathcal{O} (\alphas \alpha^3)$.

Note that all initial states have to be taken into account that lead to the same final state.
This includes the photon--photon initial state, which appears already at LO.
In the corresponding Feynman diagrams all particles are colourless, so that the photon--photon initiated contributions only receive EW and combined QCD--EW corrections, but never (pure) QCD corrections.
The EW corrections also introduce quark--photon contributions, in analogy of QCD corrections introducing quark--gluon contributions.

### 2020-08-10 paper/sec-results.tex
Add sentence about PI size of MRST2004qed
Replace 'mixed' with 'combined'

\paragraph{Experimental measurements and process features.}
We select the single-differential invariant mass distribution of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
energy of \SI{7}{\tera\electronvolt} in the high-mass region
($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
We also select the single-differential rapidity distribution, $y_{\ell\bar\ell}$, in slices of
the invariant mass of the lepton pair, $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
section~\ref{sec:pineappl-example}, 
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
Mixed-coupling QCD--EW corrections occur only at NNLO, and are therefore not
considered here. EW corrections for this process were computed in
refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

@@

The measurement is mainly driven by $\mathrm{q}\bar{\mathrm{q}}$ scattering: specifically, the
leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$)
parton luminosity, which accounts for about \SI{55}{\percent} (\SI{49}{\percent}) of the cross section
for the lowest invariant mass bins, and \SI{68}{\percent} (\SI{22}{\percent}) for the largest invariant
mass bins.\footnote{The size of these contributions may depend on the input PDF
  set. Here and in the following, we always quote results obtained from the
  \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} PDF set.}
The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
about \SI{3.6}{\percent} in the highest bin. Overall, the EW corrections range between \SI{5}{\percent}
around $M_{\ell\bar\ell}\sim \SI{150}{\giga\electronvolt}$, \SIrange{2}{3}{\percent} for intermediate invariant mass
values, $\SI{150}{\giga\electronvolt}\lesssim M_{\ell\bar\ell}\lesssim \SI{700}{\giga\electronvolt}$, and
\SIrange{15}{20}{\percent} for the largest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
$M_{\ell\bar\ell}>\SI{210}{\giga\electronvolt}$ were not included in the NNPDF3.1
analysis~\cite{Ball:2017nwa}.

>>>>

\paragraph{Experimental measurements and process features.}
We select the single-differential invariant mass distribution of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of-mass
energy of \SI{7}{\tera\electronvolt} in the high-mass region
($M_{\ell\bar\ell}>\SI{116}{\giga\electronvolt}$)~\cite{Aad:2013iua}.
We also select the single-differential rapidity distribution, $y_{\ell\bar\ell}$, in slices of
the invariant mass of the lepton pair, $M_{\ell\bar\ell}$,
measured by the CMS experiment at a centre-of-mass energy of
\SI{7}{\tera\electronvolt}~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable. As explained in
section~\ref{sec:pineappl-example}, 
the process has a single LO, $\mathcal{O}(\alpha^2)$; at NLO, the
QCD contribution is $\mathcal{O}(\alphas\alpha^2)$, while the EW contribution
is $\mathcal{O}(\alpha^3)$. Our NLO QCD computation includes the
$\mathcal{O}(\alpha^2)$ and $\mathcal{O}(\alphas\alpha^2)$ contributions, while
our NLO QCD+EW computation includes the $\mathcal{O}(\alpha^2)$, 
$\mathcal{O}(\alphas\alpha^2)$ and $\mathcal{O}(\alpha^3)$ contributions.
Combined QCD--EW corrections occur only at NNLO, and are therefore not
considered here. EW corrections for this process were computed in
refs.~\cite{Baur:2001ze,Dittmaier:2009cr}. The process receives contributions
from 13 (35) parton luminosities at NLO QCD (NLO QCD+EW),
see appendix~\ref{app:lumis} for details.

@@

The measurement is mainly driven by $\mathrm{q}\bar{\mathrm{q}}$ scattering: specifically, the
leading (next-to-leading) contribution comes from a $\mathrm{u}\bar{\mathrm{u}}$/$\mathrm{c}\bar{\mathrm{c}}$ ($\mathrm{d}\bar{\mathrm{d}}$/$\mathrm{s}\bar{\mathrm{s}}$)
parton luminosity, which accounts for about \SI{55}{\percent} (\SI{49}{\percent}) of the cross section
for the lowest invariant mass bins, and \SI{68}{\percent} (\SI{22}{\percent}) for the largest invariant
mass bins.\footnote{The size of these contributions may depend on the input PDF
  set. Here and in the following, we always quote results obtained from the
  \texttt{NNPDF31\_nlo\_as\_0118\_luxqed} PDF set.}
The PI contribution raises from about \SI{1.3}{\percent} in the lowest bin to
about \SI{3.6}{\percent} in the highest bin. For the MRST2004qed PDF set, which is used to subtract PI contributions (see section~\ref{sec:doublecounting}), the value in the largest highest bin is roughly twice as large, \SI{6.9}{\percent} (also in absolute numbers).
Overall, the EW corrections range between \SI{5}{\percent}
around $M_{\ell\bar\ell}\sim \SI{150}{\giga\electronvolt}$, \SIrange{2}{3}{\percent} for intermediate invariant mass
values, $\SI{150}{\giga\electronvolt}\lesssim M_{\ell\bar\ell}\lesssim \SI{700}{\giga\electronvolt}$, and
\SIrange{15}{20}{\percent} for the largest invariant mass bin, $M_{\ell\bar\ell}>\SI{1000}{\giga\electronvolt}$,
see figure~\ref{fig:atlaszhighmass49fb}. For this reason, the data points with
$M_{\ell\bar\ell}>\SI{210}{\giga\electronvolt}$ were not included in the NNPDF3.1
analysis~\cite{Ball:2017nwa}.
